Make any stupid plot you want

### 2020-11-23 draft/sections/math.tex
stopped at marks

\subsection{Data Space}
%%% mobias figure to show what K space and F space are?

We use a fiber bundle model to represent the data, as proposed by Butler \cite{BuildSoftwareBetter}.

@@

%%This should probably be a paragraph
\begin{description}
    \item[K] base space, connectivity of observations (discrete, continuous, etc)
    \item[F] fiber space, measurement type/group (nominal, ordinal, interval, ratio)
    \item[$\pi$] map from total space E to base space K
    \item[$\sigma$] a map from base space to values in the fiber
    \item[$\sigma(k)| k \in K $] section of values at the point k in the base space
    \item[$\Gamma$] space of sections 
\end{description}

Spivak's \cite{spivakSIMPLICIALDATABASES} formulation of the fibers as a union of named types gives a way to separate the values in the fiber by type:

\begin{figure}[h]
    \label{fig:simplex}
    \includegraphics{figures/sections/math/simplex.png}
    \caption{Simplices encode the connectivity of the data, from fully disconnected (0 simplex) observations to all observations are connected to at least 3 other observations. Higher order simplicies are outside the scope of this paper.}
\end{figure}

@@

\subsubsection{Subset \& Streaming}
i for inclusion 
%% insert diagram of U, E, etc

%%% sheaves & presheaves

\subsection{Visual Space}
%%render image
\begin{tikzcd}
    \mathbb{R}^{7} \arrow[r, hook] & H \arrow[d, "\zeta" description, bend right] \\
                                   & S \arrow[u, "\rho" description, bend right] 
\end{tikzcd}

%%% R7 in H, S base space, mostly will be trivial case H = S\times R^{7}

%% region on screen that corresponds to selection on H that corresponds to selection on S

\subsection{Artist}

%%\psi map from S to topological K...
\subsubsection{Visual Idioms: Equivalance class of artists}
Visual Idioms

\subsubsection{Visual Variable Invariance}
Tau can preserves the measurement type properties (group scales)

Will implement in code such that this happens.

>>>>

\subsection{Data Space}
\begin{figure}[ht]
    \includegraphics[width=0.5\linewidth]{figures/sections/math/mobius.png}
    \caption{write up some words here}
    \label{fig:mobius}
\end{figure}

We use a fiber bundle model to represent the data, as proposed by Butler 
\cite{butlerVectorBundleClassesForm1992,butlerVisualizationModelBased1989}.

One example of a fiber bundle is the mobius band shown in figure~\ref{fig:mobius}. A fiber bundle is a topological total space $E$ with an embedded fiber space $F$, a base space on which the fibers lie $K$ and the $\pi$ and $\sigma$ mappings between $E$ and $K$. The space of all $\sigma$ is $\Gamma$

@@

As illustrated by the mobius band example in figure~\ref{fig:mobius}, the vertical lines $F$ are the range of possible values embedded in $E$. The circle $K$ is a representation of the connectivity of the points in $E$. The function $\pi$ is the mapping from a point on a specific fiber $F_{k}|k\in K$ in $E$ to a location $k \in K$.?  
The section $\sigma$ is the mapping from locations $k$ on $K$ to points on $F_{k}$ in $E$.  (Pull this back into more specific about fig, the general is making this more confusing.)

\subsubsection{Base Space $K$}

\begin{figure}[ht]
    \label{fig:simplex}
    \includegraphics{figures/sections/math/simplex.png}
    \caption{Simplices encode the connectivity of the data, from fully disconnected (0 simplex) observations to all observations are connected to at least 3 other observations. Higher order simplicies are outside the scope of this paper.}
\end{figure}

@@

\subsubsection{Fiber Space $F$}
The fibers encode the set of all possible values each observation can take. 
Spivak's \cite{spivakSIMPLICIALDATABASES} formulation of the fibers as a union of named types gives a way to separate the values in the fiber by type:

\subsubsection{Subset \& Streaming}
$\Gamma(E)$ is the space of all points in $F$ returned by $\sigma$; therefore the points being visualized in a streaming or animation example can be considered a subset that lives on base space $U$ embedded in $K$ with the same fiber $\iota^*E$ and $\iota^*\sigma$.

\begin{tikzcd}
    \iota^\ast E \arrow[r, hook] \arrow[d]                                                                       & E \arrow[d, bend right]                       \\
    U \arrow[r, "\iota" description, hook] \arrow[u, "\iota^\ast \sigma" description, bend right, shift right=2] & K \arrow[u, "\sigma" description, bend right]
\end{tikzcd}
%%% sheaves & presheaves

\subsection{Display Space}
\begin{figure}
    \includegraphics{figures/sections/math/render.png}
    \caption{}
    \label{fig:render}
\end{figure}

A physical display space can be thought of sets of $\mathbb{R}^{7}$ tuples, where 
\begin{equation}
    \mathbb{R}^{7} = {X, Y, Z, R, G, B, A}
\end{equation}

and the sets correspond to the sections on $\S$, which is the topology of the output of the artist $A$. The space $H$ is a total space representing the predisplay space, with a fiber of $\mathbb{R}^7$ and a base space of $\S$:

\begin{tikzcd}
    \mathbb{R}^{7} \arrow[r, hook] & H \arrow[d, "\pi" description, bend right] \\
                                   & S \arrow[u, "\rho" description, bend right] 
\end{tikzcd}

In the case of 2D screens, the predisplay space is a trivial fiber bundle $$H=\mathbb{R}^{7}\times S$$. As illustrated in figure~\ref{fig:render}, a region on the screen defined by the corners $$(x_1, y_1)$$ and $$(x_2, y_2)$$ maps into a region on a 2-simplex in $S$ defined by $$(\alpha_1, \beta_1)$$ and $$(\alpha_2, \beta_2)$$. The function on the simplex $f$ returns the (R, G, B, A) value for that $(\alpha, \beta)$ pair. For a region,

\begin{equation*}
\rho(\Gamma(S)) = \int_{\alpha_1}^{\alpha_2}\int_{\beta_1}^{\beta_2}\int_{z_1}^{z_2}{R, G, B, A}  
\end{equation*}

where the R,G,B,A values are derived from the how the data values are mapped to visual characteristics. The z component of the mapping to $$\mathbb{R}^7$$ is moved to the integration because this is a trivial space representing a 2D screen; $\rho$ varies depending on $H$.

\subsection{Artist}
\begin{equation}
    A: \Gamma(E) \rightarrow \Gamma(H)
\end{equation}

\subsubsection{Screen to Data}
%%diagram: [data] -Tau->[RGVXYZ]
%%%            \ /\ / 
\begin{tikzcd}
    E \arrow[d, "\pi" description]                & H \arrow[d, "\pi" description]                                                 \\
    K \arrow[u, "\sigma" description, bend right] & S \arrow[l, "\xi" description] \arrow[u, "\rho" description, bend right]
\end{tikzcd}

The pullback $\xi$ on $S \rightarrow K$ means that the values in $E$ can be directly mapped to a simplex in $S$, which means there's a mapping from screen space back to the values.

\begin{tikzcd}
    \xi E \arrow[rr, "\tau" description] \arrow[rd, "\xi \sigma" description, bend right] &     & H \arrow[ld] \\
    & S \arrow[lu, bend right] &             
    \end{tikzcd}

\subsubsection{Marks}

\subsubsection{Visual Characteristics}
Tau can preserves the measurement type properties (group scales)

\subsubsection{Visual Idioms: Equivalance class of artists}
Visual Idioms
